\TitlePt

### 2016-03-30 paper-fatiando.tex
Add screenshot of the fatiando.org website

Fatiando a Terra (\url{http://www.fatiando.org}) aims at providing such an API
for geophysical modeling. Functions in the \texttt{fatiando} package use
compatible data and mesh formats so that the output of one modeling function
can be used as input for another. Furthermore, routines can be combined and
reused to create new modeling algorithms.  Fatiando a Terra also automates
common tasks such as griding, map plotting with Matplotlib \citep[][
\url{http://matplotlib.org}]{hunter2007}, and 3D plotting with Mayavi \citep[][
\url{http://code.enthought.com/projects/mayavi}]{ramachandran2011}.  Version
0.1\footnote{
    This was the current version in 2013 when this chapter was published in the
    conference proceedings. As of April 2016, the latest version is 0.3.}
of Fatiando a Terra is focused on gravity and magnetic methods because this is
the main focus of the developers.  However, simple ``toy'' problems for
seismology and geothermics are available and can be useful for teaching
geophysics.

@@

>>>>

Fatiando a Terra (\url{http://www.fatiando.org}, see
Figure~\ref{fig:p1-fatiando-site}) aims at providing such an API
for geophysical modeling. Functions in the \texttt{fatiando} package use
compatible data and mesh formats so that the output of one modeling function
can be used as input for another. Furthermore, routines can be combined and
reused to create new modeling algorithms.  Fatiando a Terra also automates
common tasks such as griding, map plotting with Matplotlib \citep[][
\url{http://matplotlib.org}]{hunter2007}, and 3D plotting with Mayavi \citep[][
\url{http://code.enthought.com/projects/mayavi}]{ramachandran2011}.  Version
0.1\footnote{
    This was the current version in 2013 when this chapter was published in the
    conference proceedings. As of April 2016, the latest version is 0.3.}
of Fatiando a Terra is focused on gravity and magnetic methods because this is
the main focus of the developers.  However, simple ``toy'' problems for
seismology and geothermics are available and can be useful for teaching
geophysics.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/paper-fatiando/screen-capture-fatiando-org-30-03-2016.png}
    \caption{
        Screen capture of the \url{http://www.fatiando.org} website (accessed
        30 of March 2016).
    }
    \label{fig:p1-fatiando-site}
\end{figure}
